---
title: "EDS241: Assignment 2"
author: "Connor Flynn"
date: '`r format(Sys.time(), "%m/%d/%Y")`'
output: 
  pdf_document:
    toc: false
    number_sections: yes
header-includes:
  - \setlength{\parindent}{1em}
  - \usepackage{float}
--- 

``` {r setup, echo = FALSE, message = FALSE, warning = FALSE}

# set default chunk options
knitr::opts_chunk$set(fig.width = 4, fig.height = 3, 
                      echo = TRUE, message = FALSE, warning = FALSE)


# load packages
packages=c("stargazer", "here", "tidyr", "dplyr","stringr", "janitor", 
           "cowplot", "ggplot2", "tinytex", "datasets", "tibble", "openxlsx", 
           'estimatr', "knitr", "car", "readxl")

for (i in packages) {
  if (require(i,character.only=TRUE)==FALSE) {
    install.packages(i,repos='http://cran.us.r-project.org')
  }
  else {
    require(i,character.only=TRUE)
  }
}

#devtools::install_github('rstudio/rmarkdown')
options(scipen=999) # not scientific notation


```



```{r}
data <- read_excel(here("data/NBP.xls"))
```


```{r}
Dnox_masstons_plot <- ggplot(data = data, aes(x = Dnox_masstons)) +
  geom_histogram(bins = 50)

Dnox_masstons_plot
```
```{r}
med <- median(data$PctBlack)
```

```{r}
data <- data %>%
  mutate(D = ifelse(PctBlack > med, c(1), c(0)))
  Ave_PctBlack <- data %>%
  filter(D == 1) %>%
  summarise(Ave_PctBlack = mean(PctBlack))
  
  
Ave_PctBlack
```
The average of PctBlack for counties above the median is 19.31%

```{r}
lm_robust(data = data, Dnox_masstons ~ NBP)
```

For counties where the NOx Budget Program was not implemented, the average change in annual NOx emissions from all power plants was -3.6 tons. 
For counties where the NOx Budget Program was implemented, the average change in annual NOx emissions from all power plants increased by -3.9 tons. (Resulting in an -7.5 tons average change in annual NOx emissions from all power plants)

```{r}
ggplot(data = data, aes(x = NBP, y = Dnox_masstons)) +
  geom_smooth(method = lm)
```
```{r}
regression_test <- data %>% 
  group_by(NBP) %>% 
  summarise(mean_Dnox_masstons = mean(Dnox_masstons))

regression_test
```





